### 2023-12-13 sections/4-results.tex
quad-figure in place

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{plots/fashion-mnist-knn-10.png}
    \caption{
        Algorithm performance by cardinality multiplier on fashion-mnist for $k=10$.
    }
    \label{fig:results:fashion-mnist-scaling}
\end{figure}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{plots/glove-25-knn-10.png}
    \caption{
        Algorithm performance by cardinality multiplier on glove-25 for $k=10$.  }
    \label{fig:results:glove-25-scaling}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{plots/sift-knn-10.png}
    \caption{
        Algorithm performance by cardinality multiplier on sift for $k=10$.    }
    \label{fig:results:sift-scaling}
\end{figure}

% We need to redo this plot so that we do not actually augment random datasets but instead take larger and larger 
% random datasets

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{plots/random-1000000-128-knn-10.png}
    \caption{
        Algorithm performance by cardinality multiplier on a random dataset for $k=10$.
    }
    \label{fig:results:random-scaling}
\end{figure}

>>>>

\begin{figure}
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{plots/fashion-mnist-knn-10.png}\\
\subcaption{Fashion-mnist for $k=10$.}
\label{fig:results:fashion-mnist-scaling}
\end{subfigure}%
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{plots/glove-25-knn-10.png}\\
\subcaption{Glove-25 for $k=10$.  }
\label{fig:results:glove-25-scaling}
\end{subfigure}%
\\
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{plots/sift-knn-10.png}\\
\subcaption{Sift for $k=10$.    }
\label{fig:results:sift-scaling}
\end{subfigure}%
\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=0.95\textwidth]{plots/random-1000000-128-knn-10.png}\\
\subcaption{A random dataset for $k=10$.
}
\label{fig:results:random-scaling}
\end{subfigure}%

\caption{Algorithm performance across four datasets. In each plot, the horizontal axis represents increasing cardinality (size) of the dataset, while the vertical axis represents the throughput in queries per second (higher is better).}
\end{figure}

% 
% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=3.4in]{plots/fashion-mnist-knn-10.png}
%     \caption{
%         Algorithm performance by cardinality multiplier on fashion-mnist for $k=10$.
%     }
%     \label{fig:results:fashion-mnist-scaling}
% \end{figure}

@@

% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=3.4in]{plots/glove-25-knn-10.png}
%     \caption{
%         Algorithm performance by cardinality multiplier on glove-25 for $k=10$.  }
%     \label{fig:results:glove-25-scaling}
% \end{figure}

% 
% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=3.4in]{plots/sift-knn-10.png}
%     \caption{
%         Algorithm performance by cardinality multiplier on sift for $k=10$.    }
%     \label{fig:results:sift-scaling}
% \end{figure}

% We need to redo this plot so that we do not actually augment random datasets but instead take larger and larger 
% random datasets
% 
% \begin{figure}[ht!]
%     \centering
%     \includegraphics[width=3.4in]{plots/random-1000000-128-knn-10.png}
%     \caption{
%         Algorithm performance by cardinality multiplier on a random dataset for $k=10$.
%     }
%     \label{fig:results:random-scaling}
% \end{figure}
